---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plotMissing

<!-- badges: start -->
<!-- badges: end -->

The goal of the `plotMissing` library is to allow users to easily plot the number of missing values for each column in a tibble dataset. This plot is created using the `plotMissing::plotMissing` function, which is currently (as of November 10, 2023) the only function included in this library. 

The `plotMissing` function is based partially on the [`missingNo`](https://github.com/ResidentMario/missingno) Python library (in particular, the `msno.bar` function) in Python, with many additional customization options for the resulting plot built directly into the function.

## Installation

You can install the development version of plotMissing from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/plotMissing")
```

## Examples

Because the `plotMissing` function produces a `ggplot2` object, it would be helpful to cover a few visual examples of the outputs of this function to demonstrate what the different parameters in the function represent.

```{r examples-setup}
library(plotMissing)

# Load in a dataset and coerce it to a tibble
airquality <- tibble::tibble(datasets::airquality)
```

### Basic function call

```{r plotMissing-demo-1}
plotMissing(airquality)
```

### Changing the plot with the built-in function parameters

```{r plotMissing-demo-2}
plotMissing(airquality, 
            cols = tidyselect::starts_with(c("O", "S", "T", "W")),
            count_names = c("NA", "Not NA"),
            bar_colours = c("#ABCDEF", "#FEDCBA"))
```

### Adding additional graphical parameters with the `...` argument

```{r plotMissing-demo-3}
plotMissing(airquality, 
            ggplot2::theme_classic(),
            ggplot2::labs(x = "Column Name", y = "Number of Rows",
                          fill = "NA or not?"),
            cols = tidyselect::starts_with(c("O", "S", "T", "W")),
            count_names = c("NA", "Not NA"),
            bar_colours = c("#ABCDEF", "#FEDCBA"))
```

## Future Updates

There are some future updates planned for the `plotMissing` package which are meant to improve the 'customizability' of the plots which the package generates. The future features include the following:

- Create plots for only one "group" (e.g. only display the number of missing values per column)
- Improving the language for the `count_names` and `bar_colours` parameters to make them more intuitive
- Customizing the order of the bars in the plot
- Letting the users decide whether the coordinates should be flipped
- Letting users decide which bar is on the top/left

